Appendix to Public Gender Egalitarianism: A Dataset of Dynamic Comparative

### 2022-03-23 paper/pge_appendix.Rmd
add para on overlap; drop obs_by_item2 plot

Together, the survey items in the source data were asked in `r n_countries` different countries in at least two time points over `r n_years` years, `r year_range`, yielding a total of `r n_cyi` country-year-item observations.
The number of items observed in the source data for each country-year is plotted in Figure \ref{obs_by_cy} below.
The PGE scores of country-years with more observed items are likely to be estimated more precisely.
The estimates for country-years with fewer (or no) observed items rely more heavily (or entirely) on the random-walk prior and are therefore less certain.
Figure \ref{obs_by_item2} displays the distribution of the source data in yet another way, showing the (binned) number of country-years in which both members of each pair of items is observed.

@@

```{r pge_items_table1}  
pge_items_table <- function(x) {
    items_summary %>% 
        slice(x) %>% 
        transmute(`Survey\nItem\nCode` = item,
                  `Country-Years` = as.character(n_cy),
                  `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
                  `Dispersion` = dispersion,
                  `Difficulties`= difficulties,
                  `Survey Dataset Codes` = all_surveys) %>% 
        modelsummary::datasummary_df(output = "kableExtra",
                                     note = "") %>% 
        kableExtra::column_spec(c(3, 6), width = "10em") %>% 
        kableExtra::column_spec(5, width = "5em")
}

pge_items_table(1:7) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

```{r pge_items_table2}    
pge_items_table(8:14)
```

```{r pge_items_table3}    
pge_items_table(15:23)
```

```{r pge_items_table4}    
pge_items_table(24:30)
```

```{r pge_items_table5}    
pge_items_table(31:41)
```

\pagebreak
```{r pge_items_table6}    
pge_items_table(42:50)
```

\pagebreak
```{r obs_by_cy, fig.height = 9, fig.width = 6.5, fig.cap = "Source Data Observations by Country and Year \\label{obs_by_cy}"}
dcpo_input_raw_poliwork1 %>% 
  mutate(country = str_replace(country, "’", "'")) %>% 
  distinct(country, year, item, cc_rank) %>% 
  group_by(country, year) %>% 
  summarize(n = n(),
            cc_rank = cc_rank) %>% 
  ungroup() %>% 
  distinct() %>% 
  ggplot(aes(x = year, 
             y = forcats::fct_reorder(country, cc_rank),
             fill = n)) + 
  geom_tile() +
  scale_fill_stepsn(colors = rev(hcl.colors(7, "inferno")),
                    n.breaks = 7,
                    show.limits = TRUE,
                    right = FALSE,
                    name = "Observations") +
  labs(x = NULL, y = NULL) +
  scale_x_continuous(breaks=seq(1972, 2020, 4)) +
  scale_y_discrete(position = "right") +
  theme(legend.justification=c(0, 0), 
        legend.position=c(0.01, 0.01),
        axis.text.y  = element_text(size = 7)) 
```

```{r obs_by_item2, fig.height = 9, fig.width = 6.5, fig.cap = "Joint Observations in the Source Data for Each Pair of Items \\label{obs_by_item2}"}
items_by_obs <- dcpo_input_raw_poliwork1 %>%
  distinct(country, year, item) %>%
  count(item, name = "n_obs") %>%
  arrange(desc(n_obs))

dcpo_input_raw_poliwork1 %>% 
  group_by(country, year, item) %>%
  mutate(n = sum(n)) %>% 
  distinct(country, year, item, n) %>% 
  pivot_wider(names_from = "item", values_from = "n") %>% 
  ungroup() %>% 
  select(-country, -year) %>% 
  psych::pairwiseCount() %>% 
  as.data.frame() %>%
  rownames_to_column(var = "item") %>% 
  left_join(items_by_obs) %>%  
  arrange(-n_obs) %>% 
  select(item, any_of(items_by_obs %>% pull(item)), n_obs) %>% 
  pivot_longer(cols = matches("\\d.?$"), names_to = "var2", values_to = "count") %>%
  filter(count > 0) %>% 
  mutate(item = forcats::fct_reorder(item, n_obs),
         var2 = forcats::fct_relevel(var2, rev(levels(item)))) %>% 
  ggplot(aes(x = var2, 
             y = item,
             fill = count)) + 
  geom_tile() +
  scale_fill_stepsn(colors = rev(hcl.colors(7, "inferno")),
                    breaks = c(0, 1, 10, 20, 30, 50, 100),
                    show.limits = TRUE,
                    right = FALSE,
                    trans = "log10",
                    name = "Joint\nObservations") +
  labs(x = NULL, y = NULL) +
  theme(axis.text.x  = element_text(angle = 90, vjust = .5))
```

>>>>

Together, the survey items in the source data were asked in `r n_countries` different countries in at least two time points over `r n_years` years, `r year_range`, yielding a total of `r n_cyi` country-year-item observations.
The number of items observed in the source data for each country-year is plotted in Figure \ref{obs_by_cy} below.
The PGE scores of country-years with more observed items are likely to be estimated more precisely.
The estimates for country-years with fewer (or no) observed items rely more heavily (or entirely) on the random-walk prior and are therefore less certain.

Overlap among items have not been a concern in the literature on generating latent-variable estimates of public opinion across countries and over time from sparse data, largely because the dynamic aspect of the models employed, that is, the random-walk prior, works to tie together items that do not overlap [see @Claassen2019; @Caughey2019; @Solt2020]. 
Nevertheless, the most commonly observed item in the PGE source data, `polileader4`, effectively serves as the bridge between the other items: it has overlapping country-year observations with 39 of the other 50 items (which together cover 91% of the observed country-years), and only a single item (`politics4a`, which covers 22 country-years) had no observations within a year of a `polileader4` observation.

@@

```{r pge_items_table1}  
pge_items_table <- function(x) {
  items_summary %>% 
    slice(x) %>% 
    transmute(`Survey\nItem\nCode` = item,
              `Country-Years` = as.character(n_cy),
              `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
              `Dispersion` = dispersion,
              `Difficulties`= difficulties,
              `Survey Dataset Codes` = all_surveys) %>% 
    modelsummary::datasummary_df(output = "kableExtra",
                                 note = "") %>% 
    kableExtra::column_spec(2, width = "4em") %>%     
    kableExtra::column_spec(c(3, 6), width = "11em") %>% 
    kableExtra::column_spec(5, width = "5em")
}

pge_items_table(1:2) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

```{r pge_items_table2}    
pge_items_table(3:10)
```

```{r pge_items_table3}    
pge_items_table(11:15)
```

```{r pge_items_table4}    
pge_items_table(16:24)
```

```{r pge_items_table5}    
pge_items_table(25:32)
```

```{r pge_items_table6}    
pge_items_table(33:39)
```

```{r pge_items_table7}    
pge_items_table(40:51) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

```{r obs_by_cy, fig.height = 9, fig.width = 6.5, fig.cap = "Source Data Observations by Country and Year \\label{obs_by_cy}"}
dcpo_input_raw_poliwork1 %>% 
  mutate(country = str_replace(country, "’", "'")) %>% 
  distinct(country, year, item, cc_rank) %>% 
  group_by(country, year) %>% 
  summarize(n = n(),
            cc_rank = cc_rank) %>% 
  ungroup() %>% 
  distinct() %>% 
  ggplot(aes(x = year, 
             y = forcats::fct_reorder(country, cc_rank),
             fill = n)) + 
  geom_tile() +
  scale_fill_stepsn(colors = rev(hcl.colors(6, "inferno")),
                    n.breaks = 6,
                    show.limits = TRUE,
                    right = FALSE,
                    name = "Observations") +
  labs(x = NULL, y = NULL) +
  scale_x_continuous(breaks=seq(1972, 2020, 4),
                     sec.axis = dup_axis()) +
  scale_y_discrete(position = "right") +
  theme(legend.justification=c(0, 0), 
        legend.position=c(0.01, 0.01),
        axis.text.y  = element_text(size = 7)) 
```
